# timetravelr

```{r, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE
)
```

## About

timetravelr is an R Client for the [Memento Time Travel API](http://timetravel.mementoweb.org/about/).

## Installation

```{r eval=FALSE}
require(devtools)
install_github("mementohackathon2015/timetravelr")
```

Load `timetravelr`

```{r}
library("timetravelr")
```
## Example

The [Open Archive Initiative](http://www.openarchives.org) is listing [registered OAI conforming repositories](http://www.openarchives.org/Register/BrowseSites) for many years. With the help of web archives and the Memento Time Travel API, it should be possible to assess the evolution of OAI-PMH repositoires.

### Get Timemap index

```{r}
uri <- "http://www.openarchives.org/Register/BrowseSites"
my_oai <- get_timemap(uri)
head(my_oai)
```

The timemap documents `r nrow(my_oai)`mementos.

### Get first Memento

```{r}
my_memo <- get_memento(uri, date_time = my_oai$datetime[1])
tables <- XML::readHTMLTable(my_memo$response)
my_df <- plyr::rbind.fill(tables[5])

head(my_df)
```

In the beginning, OAI initiative listed `r nrow(my_df)` OAI repos (date : `r my_oai$datetime[1]`)

### Get time series

To get a time series, we need to parse all mementos. Let's define a function

```{r}

oai_list <- function(uri = NULL, date_time = NULL) {
	my_memo <- get_memento(uri, date_time)
	tables <- XML::readHTMLTable(my_memo$response)
	out <- plyr::rbind.fill(tables[5])
	nrow(out)
}

my_oai <- my_oai[1:10,]

tt <- plyr::ldply(my_oai$datetime, oai_list, uri = "http://www.openarchives.org/Register/BrowseSites")

my_oai$counts <- tt

my_oai
```

## Get Timemap

```{r}
tt <- get_timemap("http://www.base-search.net/about/de/about_sources_date_dn.php?menu=2")

head(tt)

tt <- get_timemap("http://cnn.com")

head(tt)

```


## Redirecting URI to a Memento

```{r}
tt <- get_memento(uri = "http://cnn.com", date_time = "2011-09-11")
summary(tt)
tt$header
```

## Show Mementos for a given uri and date

```{r}
detail_memento("http://cnn.com", "2001-09-11")
```

